\begin{bibsection}

  % \item  Weiss JC and Larson E. ``La Crosse, WI: Deep Roots Community Farm.'' UWSMPH medical education day. Madison, 2015. \textbf{(Top project)}
\item  Kim Y and Weiss JC.  Harmonic mean point processes: proportional error rate minimization for obtundation prediction. \textit{Neural Information Processing Systems Workshop on Machine Learning for Health}.  Vancounver, 2019.

\item  Patel A, et al.  Machine learning algorithms in predicting hospital readmissions in sickle cell disease.  \textit{American Society of Hematology (ASH)}.  Orlando, 2019.
  
\item  Weiss JC.  High-risk and homogeneous: machine learning to identify intersections relevant for intervention.  Submitted to \textit{Neural Information Processing Systems Workshop on Machine Learning for Health}.  Montreal, 2018.
  
\item  Fillmore N, Mehta A, and Weiss JC. Bicluster phenotyping of healthcare providers, procedures, and prescriptions at scale with deep learning. \textit{Joint Workshop on Artificial Intelligence and Health}. Stockholm, 2018.
  
\item  Seymour CW, Kennedy J, Wang S, Xu Z, Chang CCH, Mi Q, Vodovotz Y, Clermont G, Viswerwaran S, Weiss JC, Cooper G, Gomez H, Kellum JA, and Angus DC. ``Feasibility of sepsis phenotyping using electronic health record data during initial emergency department care.'' \textit{American Thoracic Society}. San Diego, 2018.

\item Wingrove P, Liaw W, Petterson S, Weiss JC, and Bazemore A. ``Prescription and procedural fingerprinting: using machine learning to classify providers''. \emph{North American Primary Care Research Group}. Montreal, 2017.
  
\item  Chen G and Weiss JC. ``Survival-Supervised Topic Modeling with Anchor Words: Characterizing Pancreatitis Outcomes.'' \textit{Neural Information Processing Systems Workshop on Machine Learning for Health (ML4H)}. San Diego, 2017.
  
\item  Chen G and Weiss JC. ``Supervised Topic Models with Anchor Words for Survival Analysis and Risk Stratification of Patients with Pancreatitis.'' \textit{Society for Medical Decision Making}. Pittsburgh, 2017.
  
\item  Weiss JC and Childers S. ``Spatial statistics to evaluate player contribution in ultimate.'' \textit{Sloan Sports Analytics Conference}. Cambridge, 2014.

\item  Weiss JC and Childers S. ``Maps for reasoning in ultimate.'' \textit{ECML Workshop on Sports Analytics}. Prague, CZ, 2013.

\item  Weiss JC, Natarajan S, and Page D. ``Learning when to reject an importance sample.'' \textit{AAAI Conference Late Breaking Papers}, Bellevue, 2013.

\item  Weiss JC. ``Timeline analysis for predicting clinical events from electronic health records.'' National Library of Medicine Informatics Training Conference. Salt Lake City, 2013. \textbf{(Best talk award)}

\item  Weiss JC, Natarajan S, Peissig P, McCarty C, and Page D. ``Tree structures for continuous-time Bayesian networks: a scalable representation for medical diagnosis prediction.'' MathBio3:Modeling Symposium. Madison, 2011.

\item  Weiss JC, Berg B, Peissig P, McCarty C, and Page D. ``Clustering from overly-specific features to improve rule-based prediction.'' \textit{Neural Information Processing System (NIPS) Conference 2010 Workshop on Predictive Models In Personalized Medicine}, Vancouver, 2010.
 
\end{bibsection}


